\chapter{Introduction}

This report aims to detail the design structure for an Internet-based Library Management System (ILMS) for use with the University's campus Library system.  In order to achieve this, the system must initially be contextually analysed. This will be achieved through the creation of a use case model diagram. A use case is a list of event steps which define interactions between an actor and a system to achieve a goal. The use case model diagram will scope the ILMS functions and detail what each use case represents, as well as a justification of the design system. Furthermore the system will be behaviourally analysed by selecting one use case from the model created, then developing an activity diagram. An activity diagram displays a visual series of a flow of control, often used in business process modelling.  An activity diagram will be presented alongside a use case model detailing the justifications for the design decisions. A class model diagram will also be created in order to illustrate the design of the data structure for the ILMS. A class model diagram is a type of static structure diagram that describes the structure of a system by detailing classes along with their attributes, methods involved and the relationships among different objects. A functional workflow design will then also be created by formulating a sequence model diagram which will represent the dynamic communication of the class diagram. A sequence model diagram demonstrates the interaction between how certain objects operate with each other and the order in which this occurs. Finally this report will also detail the system component design which will be illustrated through a component model diagram to represent the reusable patterns of the system's functions. A component model diagram describes the organisation and connections of the physical components in a system.